### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@77e05d04ed5f14a0bfd7e7d2f1748de2644bddfd 🚀

@@

>>>>

In the following section, we will generate random networks, and train
four binary classifiers (as well as an ensemble model using the sum of
the outputs) on 30\% of the interaction data. Networks are generated by
picking random generality \(g\) and vulnerability \(v\) traits for
\(S = 200\) species uniformly on the unit interval, and assigning an
interaction from species \(i\) to species \(j\) if
\(0.2g_i-\xi \le v_j \le 0.2g_i+\xi\), where \(\xi\) is a constant
regulating the connectance of the networks, and varies uniformly in
\([5\times 10^{-3}, 10^{-1}]\). This model gives fully interval networks
that are close analogues to the niche model (Williams \& Martinez,
2000), but has the benefit of only relying on two features
(\(g_i, v_j\)), and having the exact same rule for all interactions. It
is, therefore, a simple case which most classifiers should be able to
learn.

@@

\leavevmode\hypertarget{ref-Williams2000SimRul}{}%
Williams, R., \& Martinez, N. (2000). Simple rules yield complex food
webs. \emph{Nature}, \emph{404}, 180--183.
\href{http://userwww.sfsu.edu/\%20}{http://userwww.sfsu.edu/}
